\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-05-01 jss/article.tex
changes

\section[Feasible Data Types]{Three Feasible Types of Data }
This package is intended to fit a multilevel model on the group-level (or unit-level) data in which each group-level (or unit-level) observation is believed to have the Normal, Poisson, or Binomial distribution. In this section, we will introduce three specific types of feasible datasets.

\subsection{Normal: 8 Schools}
Education Testing Service conducted randomized experiments in eight separate schools and obtained this dataset. It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of eight schools obtained after an analysis of covariance adjustment (Rubin, 1981).
\begin{CodeChunk}
\begin{CodeInput}
R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
\end{CodeInput}
\end{CodeChunk}

In the original paper, each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated. So, it is reasonable to think that each (group-level) coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$. \pkg{Rgbp} includes this dataset and can be called by typing `\code{R> data(schools)}' on \proglang{R}.

\subsection{Poisson: 31 Hospitals}
This dataset is about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012). It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$). The below code is an example of input based on the last ten hospital data.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
\end{CodeInput}
\end{CodeChunk}

Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger) and $\lambda_{j}$ as a true death rate per exposure. This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.

\subsection{Binomial: 18 Baseball Hitters}
This dataset contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975). Also, it has one covariate, Position, showing in which position each player was playing. For convenience, we transform this variable into a binary indicator, which is 1 if a player was a outfielder and 0 otherwise. The code below shows a way to make inputs. If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

\section[Multilevel Structure]{Multilevel Structure}
Our multilevel model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data. For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players. \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter. Users can determine one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets. 
\\

\subsection[Normal-Normal]{Normal-Normal}
\code{gbp} can construct a two-level Normal-Normal hierarchical model on the 8 school data. For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the dataset.
\begin{equation}
y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, V_{j}),
\end{equation}
\begin{equation}
\mu_{j}\vert \beta, A\stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, A),
\end{equation}

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $\beta$ and $A$ are unknown, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients. Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Also,  based on this conjugate prior distribution, it is easy to derive the corresponding posterior distribution, which is the same as the product of two distributions, (1) $\times$ (2), up to a normalizing constant.
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}),
\end{equation}
where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, 8$, are called shrinkages.

@@

where $m$ is the number of regression coefficients. For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases. The next flat prior on the second-level variance component  $A$ (or $1/r$) was chosen to bring a good repeated sampling property and for a posterior propriety under moderate conditions.
\\

@@

In this case, the most common way is to obtain an MLE of the variance component with its asymptotic Normality and then to use Delta method for asymptotic Normal distribution of shrinkage, \emph{i.e.}, $\hat{B}_{j, MLE}=B_{j}(\hat{A}_{MLE})$. But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1? If it is, why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta+\epsilon$?
\\

@@

Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only data. Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law. Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage (see (3)) and Adam's and Eve's laws are taking conditional expectation and variance over them given data, $\textbf{y}$. Since we have already estimated $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, fianlly we can estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.

@@

There are two kinds of model justification process; one is a model check and the other is a method check. The model check is for the justification of a hierarchical modeling on a specific dataset. One possible question is, ``Can this dataset benefit from such a multilevel modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
\\

@@

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (8), the distribution of each true batting average ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients. So, once we fix these hyper-parameters at specific values, we can generate true batting averages. Suppose we sampled 500 $\mathbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\mathbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (8), where $r$ and $\beta$ are given. Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-dataset and $j$ does $j$-th player. Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.  After this generating process, as for the first player, we will have 500 pairs of ($z_{i1}$, $p_{i1}$) and 500 interval estimates, $\{(\hat{p}_{i1, low}, ~\hat{p}_{i1, upp}$), $i=1, \ldots, 500\}$.
\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

\subsection{Simple Unbiased Estimates of Coverage Probabilities}
Based on the generated pseudo-datasets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th player's interval estimate from $i$-th pseudo-dataset includes $p_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking average over these indicator variables. We call it an unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.

\subsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th dataset. We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9). Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ because we know $r$ and $\beta$. Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.

\section[Example]{Example}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not). If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery. On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision to choose a hospital.
\\

@@

Assuming an additional hierarchy is reasonable, a model-fitting process begins.  Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data. Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 3.2 . For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via any regression.
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for whole observations:

@@

The output contains information about sample mean (\code{obs.mean}), caseload (\code{n}), known prior mean ($\lambda_{0}$), shrinkage ($B_{j}$), lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
\\

@@

A function ``\code{summary}'' shows selective information on hospitals and more detailed estimation result as below. To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$). On top of that, more specific estimation results, such as the estimation result of $\alpha\equiv\log(1/r)$, follow. Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a regression model and the summary of regression fit will appear.
\begin{CodeChunk}
\begin{CodeInput}
R> summary(p)
\end{CodeInput}
\begin{CodeOutput}
Main summary:

@@

  post.mode.alpha post.sd.alpha
1          -5.818         0.411
\end{CodeOutput}
\end{CodeChunk}
Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage was estimated. For example,  the shrinkage estimate of the last hospital ($\hat{B}_{31}= 0.201$) whose observed sample size is 1340,  was calculated by 336 / (336 + 1340).
\\

@@

Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean. For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.01 and caseloads ($n_{j}$) are 1 and 100 each. Do you believe that the former hospital is better than the latter and are you going to choose the former hospital? Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload. Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
\\

@@

Then, how reliable are these intervals? Does our procedure to generate interval estimates have good repeated sampling property? The following method check will answer this question. The \code{coverage} function below generates 10,000 pseudo-datasets assuming the estimated $r~(=336.37)$ as a given value. For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
\\

@@

It estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line). Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the unbiased estimate. Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular dataset has a very good repeated sampling property.
\\

@@

\subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
In this example, suppose you read the New York Times published on 26 April 1970. One article in this magazine covered 18 baseball players' batting averages through their first official 45 at-bats of the 1970 season. And then, you became interested in their batting averages over the remaining season. How could you predict? For reference, the dataset  \code{baseball} has each player's batting average over the remaining season. 
\\

First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset. Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice asymptotic properties. And it is the simplest one to estimate their true batting averages. But can we say this is the best way to predict their batting averages?
\\

@@

The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-datasets. 
\\

>>>>

\section[Feasible Data Types]{Three Feasible Types of Data }
This package is intended to fit a multilevel model on the group-level (or unit-level) data in which each group-level observation is believed to have the Normal, Poisson, or Binomial distribution. In this section, we will introduce three specific types of feasible data sets.

\subsection{Normal: 8 Schools}
Education Testing Service conducted randomized experiments in eight separate schools and obtained this data set. It contains the coaching effects on SAT scores ($y_{j}, j=1, \ldots, 8$) and standard errors ($se_{j}, j=1, \ldots, 8$) of eight schools obtained after an analysis of covariance adjustment (Rubin, 1981).
\begin{CodeChunk}
\begin{CodeInput}
R> y  <- c(12, -3, 28,  7,  1,  8, 18, -1)
R> se <- c(18, 16, 15, 11, 11, 10, 10,  9)
\end{CodeInput}
\end{CodeChunk}

In the original paper, each school's coaching effect has approximately Normal sampling distribution with known sampling variance, \emph{i.e.}, standard error of each school is assumed to be known or to be accurately estimated. So, it is reasonable to think that each school-level coaching effect is distributed as an independent Normal distribution given the unknown mean $\mu_{j}$ and known standard error:  $y_{j}\vert\mu_{j}\stackrel{ind}{\sim} \textrm{Normal}(\mu_{j}, se^{2}_{j}),~ j=1, \ldots, 8$. \pkg{Rgbp} includes this data set and can be called by typing `\code{R> data(schools)}' on \proglang{R}.

\subsection{Poisson: 31 Hospitals}
This data set is about the medical profiling evaluations for Coronary Artery Bypass Graft (CABG) surgeries of 31 New York hospitals conducted in 1992 (Morris and Lysy, 2012). It comprises of the number of deaths within a month of CABG surgeries in each hospital ($z_{j},~j=1, \ldots, 31$) and total number of patients receiving CABG surgeries (case load) in each hospital ($n_{j},~j=1, \ldots, 31$). The below code is an example of input based on the last ten hospital data.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c( 14,   9,  15,  13,  35,  26,  25,  20,   35,   27)
R> n <- c(593, 602, 629, 636, 729, 849, 914, 940, 1193, 1340)
\end{CodeInput}
\end{CodeChunk}

Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown true rate parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger) and $\lambda_{j}$ as a true death rate per exposure. This data set is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.

\subsection{Binomial: 18 Baseball Hitters}
This data set contains information about batting averages of 18 major league baseball players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975). Also, it has one covariate, Position, showing in which position each player was playing. For convenience, we transform this variable into a binary indicator, which is 1 if a player was a outfielder and 0 otherwise. The code below shows a way to make inputs. If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown true batting average $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This data set is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

\section[Multilevel Structure]{Multilevel Structure}
Our multilevel model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data. For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players. \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter. Users can determine one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their data sets. 
\\

\subsection[Normal-Normal]{Normal-Normal}
\code{gbp} can construct a two-level Normal-Normal hierarchical model on the 8 school data. For reference,  $V_{j}~(\equiv \sigma^{2}/n_{j})$ below is assumed to be known or to be accurately estimated, and subscript \emph{j} indicates \emph{j}-th school in the data set.
\begin{equation}
y_{j}\vert \mu_{j} \stackrel{ind}{\sim}\textrm{Normal}(\mu_{j}, V_{j}),
\end{equation}
\begin{equation}
\mu_{j}\vert \beta, A\stackrel{ind}{\sim}\textrm{Normal}(\mu_{0j}, A),
\end{equation}

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $\beta$ and $A$ are unknown, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients. Note that if there is no covariate then $x_{j}=1$ for an intercept term ($m=1$) and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a parameter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Also,  based on this conjugate prior distribution, it is easy to derive the corresponding posterior distribution, which is the same as the product of two distributions, (1) and (2), up to a normalizing constant.
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}),
\end{equation}
where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, 8$, are called shrinkages.

@@

where $m$ is the number of regression coefficients. For $\beta$, it is reasonable choice to take flat (non-informative) distribution because information about the location gets plentiful as the number of groups increases. The next flat prior distribution of the second-level variance component $A$ (or $1/r$) was chosen to bring a good repeated sampling property and for a posterior propriety under moderate conditions.
\\

@@

In this case, the most common way is to obtain an MLE of the variance component with its asymptotic Normality and then to use Delta method for asymptotic Normal distribution of shrinkage, \emph{i.e.}, $\hat{B}_{j, MLE}=B_{j}(\hat{A}_{MLE})$. But, is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1? If it is, why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta+\epsilon$?
\\

@@

Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only data. Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law. Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are functions of shrinkage (see (3)) and Adam's and Eve's laws are taking conditional expectation and variance over them given data, $\textbf{y}$. Since we have already estimated $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, fianlly we can estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.

@@

There are two kinds of model justification process; one is a model check and the other is a method check. The model check is for the justification of a hierarchical modeling on a specific data set. One possible question is, ``Can this data set benefit from such a multilevel modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
\\

@@

\subsection{Pseudo-data Generation Process}
Figure 1 will be helpful to understand this process. As we can see in (8), the distribution of each true batting average ($p_{j},~j=1,\ldots, 18$) depends on two hyper-parameters, $r$ and $\beta_{(m\times1)}$, where $m$ is the number of regression coefficients. So, once we fix these hyper-parameters at specific values, we can generate true batting averages. Suppose we sampled 500 $\mathbf{p}_{(18\times1)}$'s, \emph{i.e.}, $\{\mathbf{p}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ from the prior distribution in (8), where $r$ and $\beta$ are given. Then, we can also generate $\{\mathbf{z}^{(i)}_{(18\times1)},~i=1, \ldots, 500\}$ given each $p_{ij},$ where $i$ indicates $i$-th pseudo-data set and $j$ does $j$-th player. Next, \code{coverage} fits the Binomial hierarchical model 500 times on $\{(\mathbf{z}^{(i)}_{(18\times1)}, \mathbf{n}_{(18 \times 1)}),~i=1, \ldots, 500\}$ to obtain 500$\times$18 interval estimates.  After this generating process, as for the first player, we will have 500 pairs of ($z_{i1}$, $p_{i1}$) and 500 interval estimates, $\{(\hat{p}_{i1, low}, ~\hat{p}_{i1, upp}$), $i=1, \ldots, 500\}$.
\begin{figure}[h]
\begin{center}
\includegraphics[width=5cm]{process.png}
\caption{Pseudo-data generating process}
\end{center}
\end{figure}

\subsection{Simple Unbiased Estimates of Coverage Probabilities}
Based on the generated pseudo-data sets, let's define an indicator variable, $I_{ij}$, which is 1 if $j$-th player's interval estimate from $i$-th pseudo-data set includes $p_{ij}$ and 0 otherwise. One way to estimate the coverage probability is taking average over these indicator variables. We call it a simple unbiased coverage probability estimate. For example, $\bar{I}_{1}=\sum_{i=1}^{500}I_{i1}/500$ is the estimated coverage probability for the first player.

\subsection{Rao-Blackwellized Unbiased estimates of Coverage Probabilities}
Rao-Blackwellization improves accuracy of an unbiased estimator by taking conditional expectation given a sufficient statistic. Based on this idea, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th data set. We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9). Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ as long as $r$ and $\beta$ are known. Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is also unbiased but more accurate than the previous simple estimator.

\section[Examples]{Examples}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not). If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery. On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision to choose a hospital.
\\

@@

Assuming an additional hierarchy is reasonable, a model-fitting process begins.  Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$) in each hospital, the Poisson distribution would be our first choice to describe the uncertainty in our data. Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in 3.2 . For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by n):

@@

The output contains information about sample mean (\code{obs.mean}), caseload (\code{n}), known prior mean ($\lambda_{0}$), shrinkage estimate ($\hat{B}_{j}$), lower interval, posterior mean ($E(\lambda_{j}\vert \textbf{z})$), upper interval, and standard deviation of posterior distribution ($sd(\lambda_{j}\vert \textbf{z})$).
\\

@@

A function ``\code{summary}'' shows selective information on hospitals and more detailed estimation result as below. To be specific, it displays some hospitals (not all as above) with minimum, median, and maximum caseloads ($n_{j}$). On top of that, more specific estimation results, such as the estimation result of $\alpha\equiv\log(1/r)$, follow. Note that when we do not know the prior mean in advance unlike this hospital problem, \code{gbp} fits a linear regression for the Normal model, a log-linear regression for the Poisson model, or a logistic regression for the Binomial model and a summary of regression fit will appear.
\begin{CodeChunk}
\begin{CodeInput}
R> summary(p)
\end{CodeInput}
\begin{CodeOutput}
Main summary:

@@

  post.mode.alpha post.sd.alpha
1          -5.818         0.411
\end{CodeOutput}
\end{CodeChunk}
Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which is a good indicator of how valuable and informative the hypothetical second-level hierarchy is. Note that $r$ can be interpreted as the amount of prior information, although we do not know its true value. So, \code{gbp} asked data how much credit they wanted to give to this hypothetical second-level hierarchy. $\hat{r}$ = 336 is the answer from the data. It means that observed sample means of hospitals whose caseloads are less than 336 will shrink toward the prior mean (0.020) more than 50\%. 
\\

For example, the shrinkage estimate of the first hospital ($\hat{B}_{1}= 0.834$) was calculated by 336 / (336 + 67), where 67 is its caseload ($n_{1}$), and its posterior mean is $(1-0.834)*0.045 + 0.834 * 0.020=0.024$. As for this hospital, using more information from the prior distribution makes sense because its observed amount of information (67) is far less than the amount of state-level information (336).
\\

@@

Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean. For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.01 and caseloads ($n_{j}$) are 1 and 100 each. Do you believe that the former hospital is better than the latter and are you going to choose the former hospital? Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload. Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this data set.
\\

@@

Then, how reliable are these intervals? Does our procedure to generate interval estimates have good repeated sampling property? The following method check will answer this question. The \code{coverage} function below generates 10,000 pseudo-data sets assuming the estimated $r~(=336.37)$ as a given value. For reference, we can try any other value of $r$, for example $r=200$, by replacing below code with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 10000)}.
\\

@@

It estimated coverage probabilities by unbiased estimates (a blue dashed line) and Rao-Blackwellized estimates (a red line). Both lines are indistingishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.951 from the Rao-Blackwellized estimate and 0.95 from the unbiased estimate. Considering this result, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular data set has a very good repeated sampling property.
\\

@@

\subsection[Unknown Second-level Mean and One Covariate]{18 Baseball Players: Unknown Prior Mean and One Covariate}
In this example, suppose you read the New York Times published on 26 April 1970. One article in this magazine covered 18 baseball players' batting averages through their first official 45 at-bats of the 1970 season. And then, you became interested in their batting averages over the remaining season. How could you predict? For reference, the data set  \code{baseball} has each player's batting average over the remaining season. 
\\

First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this data set. Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice asymptotic properties. And it is the simplest one to estimate their true batting averages. But can we say this is the best way to predict their batting averages?
\\

@@

The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-data sets. 
\\
